Comparison of large-scale citizen science data and long-term study data for phenology modeling

### 2018-10-23 manuscript/supplement_images.tex
updated appendix2 latex file

\usepackage{graphicx}
\usepackage{a4wide}
\usepackage{adjustbox}
\usepackage{float}
\usepackage{lineno}
\usepackage{setspace}
  \doublespacing
\usepackage[document]{ragged2e}

@@

\textbf{Figure S1}: Sensitivity test results from using a 15 versus 30 day cutoff between the 'yes' and most recent 'no' in the USA-NPN dataset. Each point represents the value of a single parameter for one of eight models for 33 species and phenophases in the USA-NPN dataset. Note only 33 comparisons were possible here as the stricter 15 day cutoff resulted in three of the species not having sufficient observations.

>>>>

\usepackage{graphicx}
\usepackage{a4wide}
\usepackage{adjustbox}
\usepackage{float}
\usepackage{lineno}
\usepackage{setspace}
  \doublespacing

@@

\textbf{Figure S1}: Sensitivity test results from using a 15 versus 30 day cutoff between the 'yes' and most recent 'no' in the USA-NPN dataset. Each point represents the value of a single parameter for one of eight models for 32 unique species/phenophase combinations. This is from 23 species with varying combinations of the budburst and flowering phenophases (see Table S1). Only 32 comparisons were possible here as the stricter 15 day cutoff resulted in three species/phenophase combinations not having sufficient observations. This figure does not include any data from the LTER datasets. Note that the primary analysis states 35 combinations using the 15 day cutoff. This is because 3 species are duplicated in the Harvard Forest and Hubbard Brook datasets, thus 3 extra comparisons are available for the primary analysis.
